On Verification Patterns for Low-Level Systems via Modal Abstractions

### 2025-09-12 paper.tex
+

To explain our ideas in the general systems understanding, we briefly recap some of the background and themes our ideas build on again, casting them in a certain way to bring out the relevance of our philosophy.
\subsection{Encoding Modalities in Program Logics}

\paragraph{Encoding Hoare Triples} With Pratt's original representation, we can encode where a Hoare triple $\{P\}C\{Q\}$ is encoded as $P\rightarrow[C](Q)$. However, this modal representation requires to be given a semantics which is in terms of an underlying model.

On the other hand the underlying model for \textsf{Iris}~\cite{jung2018iris} would be a collection of \textsc{CMRA}s ---
an algebraic cousin of a BI-algebra~\cite{ohearn1999bunched}.
This is the case for \textsf{Iris}'s one built-in modality for step-indexing~\cite{nakano-00}.
However in general, many modalities can be given proof-theoretic semantics directly within a logic. 
This is the case for \textsf{Iris}'s weakest precondition modality (which is defined within the \textsf{Iris} 
logic itself) , as well as for a wide range of other modalities in the 
literature~\cite{restall2002introduction}. These modalities are typically multi-modal, 
with a form of roughly $M~\overline{ctxt}~\phi\triangleq\ldots\rightarrow \phi~\overline{ctxt}$. 
\paragraph{Shallow Modalities in Iris Separation Logic}
\label{sec:modal_in_iris}
In a substructural setting~\cite{restall1993modalities,krebbers2017essence} the implication $\rightarrow$ 
is typically replaced with substructural implication $\sepimp$.

>>>>

To explain our ideas in the general systems understanding, we briefly recap some of the background and themes our ideas build on again, casting them in a certain way to bring out the relevance of our philosophy.
\subsection{Encoding Modalities in Program Logics}
Program logics which would like to enjoy modal propositions need to have an underlying model that allows encoding of the propositions. Since . Kripke model is the model all program logics directly or indirectly, sits on. Kripke model can be roughly seen as a triple of set of worlds (e.g., program states), a binary relation between worlds (e.g., transition relations between states) and a state interpretation function.  
\paragraph{Encoding Hoare Triples} With Pratt's original representation, we can encode where a Hoare triple $\{P\}C\{Q\}$ is encoded as $P\rightarrow[C](Q)$. However, this modal representation requires to be given a semantics which is in terms of an underlying model.

Conventionally, a Kripke model with its constituent must be picked. Gordon give a Kripke model for an actor-based hybrid modal logic ~\cite{} in which the transition relation is indexed by a particular command and a particular actor. Wagner et.al. takes the similar approach for the design of their program logic for reference counted memory.

The underlying model for \textsf{Iris}~\cite{jung2018iris} would be a collection of \textsc{CMRA}s ---
an algebraic cousin of a BI-algebra~\cite{ohearn1999bunched}.
This is the case for \textsf{Iris}'s one built-in modality for step-indexing~\cite{nakano-00}.
However in general, many modalities can be given proof-theoretic semantics directly within a logic. 
This is the case for \textsf{Iris}'s weakest precondition modality (which is defined within the \textsf{Iris} 
logic itself) , as well as for a wide range of other modalities in the 
literature~\cite{restall2002introduction}. These modalities are typically multi-modal, 
with a form of roughly $M~\overline{ctxt}~\phi\triangleq\ldots\rightarrow \phi~\overline{ctxt}$. 
\paragraph{Shallow Modalities in Iris Separation Logic}
\label{sec:modal_in_iris}
In a substructural setting~\cite{restall1993modalities,krebbers2017essence} the implication $\rightarrow$ 
is typically replaced with substructural implication $\sepimp$.
